Compiling refinement types to dependent types

### 2020-07-23 tex/paper.tex
Add a %TODO about the context not actually coinciding
Reuse Γ in definition of \hat e_i
TWF-Conj translation defined

    We do not mention the premises of the translated rule.
    By \cref{lma:non_dep_pair_typing}
    $(\hat B, \unitc \equiv \unitc)$ has type $\star$ in $\nonterm{GC}$
    if $\hat B$ and $\unitc \equiv \unitc$ are well-typed in $\nonterm{GC}$,
    which, in turn, is easily checked.
    Thus, there exists a derivation of $\nonterm{GC} \vdash (\hat B, \unitc \equiv \unitc) : *$,
    and it is effectively constructible~--- we just omit it for brevity.
  \item \textsc{TWF-Base}.
    \begin{align*}
      & \inferrule{\nonterm G \ctxok \\\\
                   \nonterm G ' \vdash \nonterm{es}_1 : \{ v_2 : B' | \nonterm{r}_1 \} \\\\
                   \nonterm G ' \vdash \nonterm{es}_2 : \{ v_2 : B' | \nonterm{r}_2 \} \\\\
                   \gterm x \fresh}
                  {\nonterm G \vdash \{ v : B | \nonterm{es}_1 = \nonterm{es}_2 \}}
          \longmapsto
        \inferrule{\Tranterm(\nonterm G ' \vdash \nonterm{es}_1 : \{ v_2 : B' | \nonterm{r}_1 \}) \\\\
                   \Tranterm(\nonterm G ' \vdash \nonterm{es}_2 : \{ v_2 : B' | \nonterm{r}_2 \}) \\\\
                   \gterm x \fresh \\\\
                   \cdots}
                  {\nonterm{GC} \vdash (v : \hat B \dast \lambda v : \hat B. \nonterm{ec}_1 \equiv \nonterm{ec}_2) : \star}, \\
      \text{where}~&\nonterm{GC} = \Tranctx(\nonterm G \ctxok), \\
                   &\nonterm G ' = \nonterm G , v : \{ v_1 : B | \top \}, \\
                   &\nonterm{ec}_i =
                     \tranterm(\nonterm G , x : \{ v_1 : B | \top \} \vdash \nonterm{es}_i : \{ v_2 : B' | \nonterm{r}_i \}).
    \end{align*}

@@

    Just as in the previous case, the extra derivations and premises corresponding to the considerations above
    are omitted and denoted by $\cdots$.
  \item \textsc{TWF-Arr}.
    \begin{align*}
      & \inferrule{\nonterm G \ctxok \\\\
                   \nonterm G \vdash \nonterm{ts}_1 \\
                   \nonterm G , \gterm x : \nonterm{ts}_1 \vdash \nonterm{ts}_2}
                  {\nonterm G \vdash (\gterm x : \nonterm{ts}_1) \rightarrow \nonterm{ts}_2}
          \longmapsto
        \inferrule{\Tranty(\nonterm G \vdash \nonterm{ts}_1) \\
                   \Tranty(\nonterm G , \gterm x : \nonterm{ts}_1 \vdash \nonterm{ts}_2)}
                  {\nonterm{GC} \vdash \Pi x : \nonterm{tc}_1. \nonterm{tc}_2 : \star}, \\
      \text{where}~&\nonterm{GC} = \Tranctx(\nonterm G \ctxok),                                         \\
                   &\nonterm{tc}_1 = \tranty(\nonterm G \vdash \nonterm{ts}_1),                         \\
                   &\nonterm{tc}_2 = \tranty(\nonterm G , \gterm x : \nonterm{ts}_1 \vdash \nonterm{ts}_2).
    \end{align*}

>>>>

    We do not mention the premises of the translated rule.
    By \cref{lma:non_dep_pair_typing}
    $(\hat B, \unitc \equiv \unitc)$ has type $\star$ in $\nonterm{GC}$
    if $\hat B$ and $\unitc \equiv \unitc$ are well-typed in $\nonterm{GC}$,
    which, in turn, is easily checked.
    Thus, there exists a derivation of $\nonterm{GC} \vdash (\hat B, \unitc \equiv \unitc) : *$,
    and it is effectively constructible~--- we just omit it for brevity.
  \item \textsc{TWF-Base}.
    \begin{align*}
      & \inferrule{\nonterm G \ctxok \\\\
                   \nonterm G ' \vdash \nonterm{es}_1 : \{ v_2 : B' | \nonterm{r}_1 \} \\\\
                   \nonterm G ' \vdash \nonterm{es}_2 : \{ v_2 : B' | \nonterm{r}_2 \} \\\\
                   \gterm x \fresh}
                  {\nonterm G \vdash \{ v : B | \nonterm{es}_1 = \nonterm{es}_2 \}}
          \longmapsto
        \inferrule{\Tranterm(\nonterm G ' \vdash \nonterm{es}_1 : \{ v_2 : B' | \nonterm{r}_1 \}) \\\\
                   \Tranterm(\nonterm G ' \vdash \nonterm{es}_2 : \{ v_2 : B' | \nonterm{r}_2 \}) \\\\
                   \gterm x \fresh \\\\
                   \cdots}
                  {\nonterm{GC} \vdash (v : \hat B \dast \lambda v : \hat B. \nonterm{ec}_1 \equiv \nonterm{ec}_2) : \star}, \\
      \text{where}~&\nonterm{GC} = \Tranctx(\nonterm G \ctxok), \\
                   &\nonterm G ' = \nonterm G , v : \{ v_1 : B | \top \}, \\
                   &\nonterm{ec}_i =
                     \tranterm(\nonterm G ' \vdash \nonterm{es}_i : \{ v_2 : B' | \nonterm{r}_i \}).
    \end{align*}

@@

    %TODO the { v : B | T } in the Γ' desugars to a dependent pair, yet we use λv : \hat B — note the naked base type.
    %Figure out how to best fix this.

    Just as in the previous case, the extra derivations and premises corresponding to the considerations above
    are omitted and denoted by $\cdots$.
  \item \textsc{TWF-Conj}.
    \begin{align*}
      & \inferrule{\nonterm G \ctxok \\\\
                   \nonterm G \vdash \{ v : B | \nonterm{r}_1 \} \\
                   \nonterm G \vdash \{ v : B | \nonterm{r}_2 \}}
                  {\nonterm G \vdash \{ v : B | \nonterm{r}_1 \land \nonterm{r}_2 \}}
          \longmapsto
        \inferrule{\cdots \\\\
                   \Tranty(\nonterm G \vdash \{ v : B | \nonterm{r}_1 \}) \\
                   \Tranty(\nonterm G \vdash \{ v : B | \nonterm{r}_2 \})}
                  {\nonterm{GC} \vdash (v : \hat B \dast \lambda v : \hat B. (P_1 v, P_2 v)) : \star}, \\
      \text{where}~&\nonterm{GC} = \Tranctx(\nonterm G \ctxok),                                         \\
                   &P_1 \text{~s.t.~} (v : \hat B \dast \lambda v : \hat B. P_1 v) = \tranty(\nonterm G \vdash \{ v : B | \nonterm{r}_1 \}),  \\
                   &P_2 \text{~s.t.~} (v : \hat B \dast \lambda v : \hat B. P_2 v) = \tranty(\nonterm G \vdash \{ v : B | \nonterm{r}_2 \}).
    \end{align*}

    The proof of the right-hand side being well-defined goes similarly to the cases considered previously
    with an extra step.
    Namely, note that the last two ``patterns'' on the left-hand side are irrefutable:
    it can be seen by direct inspection and inductive reasoning that $\tranty$ always yields a pair
    for a derivation of the form $\nonterm G \vdash \{ v : B | \nonterm{r} \}$.
    Thus we can take the predicate components $P_1, P_2$ out from the corresponding dependent pairs
    and repack them obtaining $\lambda v : \hat B. (P_1 v, P_2 v)$.
  \item \textsc{TWF-Arr}.
    \begin{align*}
      & \inferrule{\nonterm G \ctxok \\\\
                   \nonterm G \vdash \nonterm{ts}_1 \\
                   \nonterm G , \gterm x : \nonterm{ts}_1 \vdash \nonterm{ts}_2}
                  {\nonterm G \vdash (\gterm x : \nonterm{ts}_1) \rightarrow \nonterm{ts}_2}
          \longmapsto
        \inferrule{\Tranty(\nonterm G \vdash \nonterm{ts}_1) \\
                   \Tranty(\nonterm G , \gterm x : \nonterm{ts}_1 \vdash \nonterm{ts}_2)}
                  {\nonterm{GC} \vdash \Pi x : \nonterm{tc}_1. \nonterm{tc}_2 : \star}, \\
      \text{where}~&\nonterm{GC} = \Tranctx(\nonterm G \ctxok),                                         \\
                   &\nonterm{tc}_1 = \tranty(\nonterm G \vdash \nonterm{ts}_1),                         \\
                   &\nonterm{tc}_2 = \tranty(\nonterm G , \gterm x : \nonterm{ts}_1 \vdash \nonterm{ts}_2).
    \end{align*}
